ZPY: Open Source Synthetic Data for Computer Vision

### 2021-08-05 docs/paper/paper.tex
wording cleanup

Biased datasets result in biased algorithms. The nature of statistical learning methods means that training on these biased datasets will result in a biased model since a model is only as good as the data on which it is trained. The pervasive use of data-driven algorithms has complex social implications: from racial facial recognition (citation: https://nvlpubs.nist.gov/nistpubs/ir/2019/NIST.IR.8280.pdf), to predictive policing systems that act to confirm and deepen existing biases (citation: https://www.technologyreview.com/2020/07/17/1005396/predictive-policing-algorithms-racist-dismantled-machine-learning-bias-criminal-justice/). 
\subsection{Privacy}

@@

\begin{lstlisting}[language=Python,caption={Generating a dataset using the zpy python API.},label={lst:api}]
import zpy
zpy.generate()
\end{lstlisting}

\begin{lstlisting}[language=bash,caption={Generating a dataset using the zpy CLI},label={lst:cli}]
zpy create dataset "hello world dataset" my_sim num_images 1000
\end{lstlisting}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{results.png}
	\caption{Each type of domain randomization is used to create a fully synthetic dataset, which is used to fine-tune a pre-trained model on the task of package detection. Results of the model on a manually labeled test dataset of real images are compared.}
	\label{fig:results}
\end{figure}

@@

To put into practice what this paper has explained, we present a simple example of how synthetic data can be used to train a computer vision model. In this example, we train a detection model which predicts the bounding boxes for cardboard packages and parcels in images. In section \ref{sec:domainrandomization} we explore how domain randomization in different aspects of the simulation can affect final model performance.

We used a variant of Faster R-CNN implemented in PyTorch as part of the Detectron2 model zoo \cite{wu2019detectron2}. Training was done on a single Nvidia GeForce RTX 3090, with each training run lasting at most an hour: this experiment consisted only of fine-tuning a model pre-trained on ImageNet as opposed to training a model from scratch. We sweeped over various learning rates and used the largest batch size we could given our GPU memory, model size, and image size. We picked the best performing permutation of hyperparameters when comparing results, using APm on a holdout test dataset of real images.

@@

\begin{itemize}
	\item \lstinline{package_sim_dr_light} - Synthetic dataset of 512 images. Domain randomization is applied to lighting only.
	\item \lstinline{package_sim_dr_mats} - Synthetic dataset of 512 images. Domain randomization is applied to materials only.
	\item \lstinline{package_sim_dr_bg} - Synthetic dataset of 512 images. Domain randomization is applied to background only.
	\item \lstinline{package_sim_dr_all} - Synthetic dataset of 512 images. Domain randomization is applied to lighting, background, and materials.
\end{itemize}

>>>>

Biased datasets result in biased algorithms. The nature of statistical learning methods means that training on these biased datasets will result in a biased model since a model is only as good as the data on which it is trained. The pervasive use of data-driven algorithms has complex social implications: from racial facial recognition \cite{fvrt}, to predictive policing systems that act to confirm and deepen existing biases \cite{predictivepolicing}.

\subsection{Privacy}

@@

\begin{lstlisting}[language=Python,caption={Generating a dataset of 1000 images using the zpy python API.},label={lst:api}]
import zpy
zpy.generate("hello world dataset", 1000)
\end{lstlisting}

\begin{lstlisting}[language=bash,caption={Generating a dataset of 1000 images using the zpy CLI},label={lst:cli}]
zpy create dataset "hello world dataset" my_sim num_images 1000
\end{lstlisting}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{results.png}
	\caption{(Left) Sample images from synthetic training datasets with different kinds of domain randomization: lighting, background, material, and all of the above. (Right) Bounding box predictions of a model fine-tuned on the corresponding synthetic dataset along with confidence for each detection, false positives shown for context.}
	\label{fig:results}
\end{figure}

@@

To put into practice what this paper has explained, we present a simple example of how synthetic data can be used to train a computer vision model. In this example, we train a detection model which predicts the bounding boxes for cardboard packages and parcels in images. In section \ref{sec:trainingmodel} we provide some details on the model and training setup. In section \ref{sec:domainrandomization} we explore how domain randomization in different aspects of the simulation can affect final model performance.

\subsection{Training and Model Specs}
\label{sec:trainingmodel}

We used several variants of Faster R-CNN implemented in PyTorch as part of the Detectron2 model zoo \cite{wu2019detectron2}. Training was done on a single Nvidia GeForce RTX 3090, with each training run lasting at most several thousand iterations, which corresponds to at most 10 epochs given the training dataset size of 512 images. For this experiment we fine-tune a model pre-trained on the COCO detection task as opposed to training the model from scratch. This type of transfer learning is common when using machine learning in the real world due to the quick training speed and relatively good performance. We sweeped over various learning rates and used the largest batch size we could given our GPU memory, model size, and image size. We picked the best performing permutation of hyperparameters when comparing results, using APm on a holdout test dataset of real images.

@@

\begin{itemize}
	\item \lstinline{package_sim_dr_light} - Synthetic dataset of 512 images. Domain randomization is applied to lighting only. The position of a sun light object in the scene, as well as the intensity of the light, is randomized within a range for every image
	\item \lstinline{package_sim_dr_mats} - Synthetic dataset of 512 images. Domain randomization is applied to materials only. The material of each individial package is created in each image, starting with a randomly chosen texture from a library of thousands of textures scraped from the internet. Several properties of the material, such as specular, metallic, and roughness are then jittered within a broad range.
	\item \lstinline{package_sim_dr_bg} - Synthetic dataset of 512 images. Domain randomization is applied to background only. Each image is rendered with a different HDRI, which is chosen from a library of hundreds of HDRIs scraped from the internet.
	\item \lstinline{package_sim_dr_all} - Synthetic dataset of 512 images. Domain randomization is applied to lighting, background, and materials.
\end{itemize}
